---
title: "heart-logitReg-train_test"
author: "Haeyoon Chang"
date: "11/28/2020"
output: pdf_document
---

LogitRegression for Selecting Features

Description of parameters: 
- age: age in years (29 - 77)
- sex: 1 = male; 0 = female (0, 1)
- cp: chest pain type (0, 1, 2, 3) 
- trestbps: resting blood pressure (in mm Hg on admission to the hospital)
- chol: serum cholesterol in mg/dl
- fbs: fasting blood sugar > 120 mg / dl (1 = true, 0 = false)
- restecg: resting electrocardiographic results (0, 1, 2)
- thalach: maximum heart rate achieved
- exang: exercise induced anigma (1 = yes; 0 = no)
- oldpeak: ST depression induced by exercise relative to rest 
- slope: the slope of the peak exercise ST segment
- ca: number of major vessels colored by flourospy (0-3)
- thal: 3 = normal; 6 = fixed defect; 7 = reversible defect 
- target: presence of heart diseases in the patient (1 = yes, 0 = no)

```{r}
# import data 
training.data.raw <- read.csv("heart.csv", header=T, na.strings=c(""))

# detect if there's any na 
# sapply(training.data.raw, function(x) sum(is.na(x)))

# count how many unique values in each column
sapply(training.data.raw, function(x) length(unique(x)))

# select subset of the original dataset 
data <- training.data.raw
data <- transform(
  data,
  age=as.integer(age),
  sex=as.factor(sex),
  cp=as.factor(cp),
  trestbps=as.integer(trestbps),
  chol=as.integer(chol),
  fbs=as.factor(fbs),
  restecg=as.factor(restecg),
  thalach=as.integer(thalach),
  exang=as.factor(exang),
  oldpeak=as.numeric(oldpeak),
  slope=as.factor(slope),
  # ca=as.factor(ca),
  # thal=as.factor(thal),
  target=as.factor(target)
)
# sapply(data, class)
summary(data)
```

```{r}
library(boot)
library(ROCR)

# let's split the train and test data later...
shuffled <- data[sample(nrow(data)),]
# train <- shuffled[1:228,]
# test <- shuffled[229:303,]

# create 10 equally size folds
k = 5
folds <- cut(seq(1, nrow(data)), breaks=k, labels=FALSE)

# empty R x 2 matrix for bootstrap results
CV = matrix(nrow=k, ncol = 2, dimnames = list(paste('Sample', 1:k), c("auc_train", "auc_test")))

for (i in 1:k) {
  # segment the data by fold using the which() function
  testIndexes = which(folds==i, arr.ind=TRUE)
  train = shuffled[-testIndexes,]
  test = shuffled[testIndexes,]
  
  # model

  # train
  logit <- glm(target ~ sex + cp + trestbps + thalach + exang + ca + thal, family=binomial(link='logit'), data=train)

  summary(logit)
  coef = coef(logit)
  
  # test 

  # fitted.results <- predict(logit, newdata=test, type='response')
  # fitted.results <- ifelse(fitted.results >0.5, 1, 0)
  # pred = fitted.results
  # actual = test$target
  # result = data.frame(pred, actual)
  # 
  # misClassificError <- mean(fitted.results != test$target)
  # print(paste('Accuracy', 1 - misClassificError))

  # score the same training data set on which the model was fit
  prob = predict.glm(logit, type = 'response', newdata = test)
  pred = prediction(prob, test$target)
  print(mean(pred))

  # AUC
  auc = performance(pred, "auc")@y.values[[1]][1]

  # plot the ROC curve
  perf <- performance(pred, "tpr", "fpr")
  plot(perf, col="navyblue", cex.main=1,
       main= paste("Logistic Regression ROC Curve: AUC =", round(auc,3)))
  abline(a= 0, b = 1, col='darkorange1')
  

  # apply model to original data
  prob1 = predict(logit, type='response', train)
  pred1 = prediction(prob1, train$target)
  auc1 = performance(pred1, "auc")@y.values[[1]][1]
  CV[i, 1] = auc1

  # apply model to bootstrap data
  prob2 = predict(logit, type='response', test)
  pred2 = prediction(prob2, test$target)
  auc2 = performance(pred2, "auc")@y.values[[1]][1]
  CV[i, 2] = auc2
}

avg_train_auc = sum(CV[,1])/k
avg_test_auc = sum(CV[,2])/k

(CV)
(avg_train_auc)
(avg_test_auc)
```


