---
title: "heart-logitReg-AllData"
author: "Haeyoon Chang"
date: "11/28/2020"
output: pdf_document
---

LogitRegression for Selecting Features

Description of parameters: 
- age: age in years (29 - 77)
- sex: 1 = male; 0 = female (0, 1)
- cp: chest pain type (0, 1, 2, 3) 
- trestbps: resting blood pressure (in mm Hg on admission to the hospital)
- chol: serum cholesterol in mg/dl
- fbs: fasting blood sugar > 120 mg / dl (1 = true, 0 = false)
- restecg: resting electrocardiographic results (0, 1, 2)
- thalach: maximum heart rate achieved
- exang: exercise induced anigma (1 = yes; 0 = no)
- oldpeak: ST depression induced by exercise relative to rest 
- slope: the slope of the peak exercise ST segment
- ca: number of major vessels colored by flourospy (0-3)
- thal: 3 = normal; 6 = fixed defect; 7 = reversible defect 
- target: presence of heart diseases in the patient (1 = yes, 0 = no)

```{r}
# import data 
training.data.raw <- read.csv("heart.csv", header=T, na.strings=c(""))

# detect if there's any na 
# sapply(training.data.raw, function(x) sum(is.na(x)))

# count how many unique values in each column
sapply(training.data.raw, function(x) length(unique(x)))

# select subset of the original dataset 
data <- training.data.raw
data <- transform(
  data,
  age=as.integer(age),
  sex=as.factor(sex),
  cp=as.factor(cp),
  trestbps=as.integer(trestbps),
  chol=as.integer(chol),
  fbs=as.factor(fbs),
  restecg=as.factor(restecg),
  thalach=as.integer(thalach),
  exang=as.factor(exang),
  oldpeak=as.numeric(oldpeak),
  slope=as.factor(slope),
  # ca=as.factor(ca),
  # thal=as.factor(thal),
  target=as.factor(target)
)
# sapply(data, class)
summary(data)
```

```{r}
library(boot)



# let's split the train and test data later...
# shuffled <- data[sample(nrow(data)),]
# train <- shuffled[1:228,]
# test <- shuffled[229:303,]

# model
# set.seed(304)

# data processed as continuous
# logit <- glm(target ~ sex + cp + trestbps + thalach + exang + ca + thal, family=binomial(link='logit'), data=train)

# all 14 variables included
# logit <- glm(target ~., family=binomial(link='logit'), data=data)

# data processed as discrete (categorical values)
logit <- glm(target ~ sex + cp + trestbps + thalach + exang + ca + thal, family=binomial(link='logit'), data=data)

summary(logit)
coef = coef(logit)
```

```{r}
R = 1000                 # number of bootstrap samples
n = nrow(data)           # sample size
k = length(coef(logit))   # number of coefficients

# set up a empty R x n matrix B
B = matrix(nrow = R, ncol = k, dimnames = list(paste("Sample", 1:R), names(coef(logit))))

# loop R times
# set.seed(111)
for (i  in 1:R){
  # sample credit data with replacement
  boot.data = data[sample(x = 1:n, size = n, replace=TRUE),]
  # fit the model on the bootstrapped sample
  boot.logit = glm(logit$formula, data = boot.data, family = binomial(link = "logit"))
  
  # store the coefficients
  if (length(coef(boot.logit)) == k){
    B[i, ] = coef(boot.logit)
  } else {
    # when the # of coefficients calculated < spaces assigned in matrix
    coef_len = length(coef(boot.logit))
    for (j in 1:coef_len) {
      B[i,j] = coef(boot.logit)[j]
    }
  }
}
```

```{r}
for (i in 1:k){
  hist(B[,i], main = paste("Histogram of ", colnames(B)[i]))
  print(mean(B[,i]))
}
```

```{r}
# calculate the p-value
for (i in 1:k){
  a = sum(B[,i] >= coef[i], na.rm=TRUE)/R
  print(a)
}
# null hypothesis: theta == theta
(a)
```
```{r}
fitted.results <- predict(logit, newdata=data, type='response')
fitted.results <- ifelse(fitted.results >0.5, 1, 0)
pred = fitted.results
actual = data$target
result = data.frame(pred, actual)

misClassificError <- mean(fitted.results != data$target)
print(paste('Accuracy', 1 - misClassificError))
```



Validation of Model Prediction Accuracy
```{r}
library(ROCR)

# score the same training data set on which the model was fit
prob = predict.glm(logit, type = 'response', newdata = data)
pred = prediction(prob, data$target)

# AUC
auc = performance(pred, "auc")@y.values[[1]][1]

# plot the ROC curve
perf <- performance(pred, "tpr", "fpr")
plot(perf, col="navyblue", cex.main=1,
     main= paste("Logistic Regression ROC Curve: AUC =", round(auc,3)))
abline(a= 0, b = 1, col='darkorange1')
```

```{r}
R = 100                # number of bootstrap samples
n = nrow(data)         # sample size

# empty R x 2 matrix for bootstrap results
B = matrix(nrow=R, ncol = 2, dimnames = list(paste('Sample', 1:R), c("auc_orig", "auc_boot")))

# set.seed(701)
for(i in 1:R) {
  
  # sample target data with replacement
  data.boot = data[sample(x = 1:n, size = n, replace=TRUE),]
  
  # fit the model on bootstrap sample
  logit.boot = glm(logit$formula, data=data.boot, family=binomial(link ="logit"))
  
  # apply model to original data
  prob1 = predict(logit.boot, type='response', data)
  pred1 = prediction(prob1, data$target)
  auc1 = performance(pred1, "auc")@y.values[[1]][1]
  B[i, 1] = auc1
  
  # apply model to bootstrap data
  prob2 = predict(logit.boot, type='response', data.boot)
  pred2 = prediction(prob2, data.boot$target)
  auc2 = performance(pred2, "auc")@y.values[[1]][1]
  B[i, 2] = auc2
}

avg_insample_auc = sum(B[,1])/R
avg_bootstrap_auc = sum(B[,2])/R

(B)
(avg_insample_auc)
(avg_bootstrap_auc)
```

